\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{float}
\usepackage{subcaption}
\usepackage{geometry}
\geometry{
    a4paper,
    total={170mm,257mm},
    left=20mm,
    right=20mm,
    top=20mm,
}
\usepackage{listings} % code listings
\lstset{framextopmargin=0pt,frame=lines}
\lstset{
    language=Matlab,
    basicstyle=\footnotesize\ttfamily,
    breaklines=true,
    tabsize=4,
    keepspaces=true,
    columns=flexible,
    % backgroundcolor=\color[gray]{0.9},
    frame=single,
    breaklines=true,%
    morekeywords={matlab2tikz},
    keywordstyle=\color{blue},%
    morekeywords=[2]{1}, keywordstyle=[2]{\color{black}},
    identifierstyle=\color{black},%
    stringstyle=\color{mylilas},
    commentstyle=\color{mygreen},%
    showstringspaces=false,%without this there will be a symbol in the places where there is a space
    numbers=left,
    numberstyle={\tiny \color{black}},% size of the numbers
    numbersep=9pt, % this defines how far the numbers are from the text
    emph=[1]{for,end,break},emphstyle=[1]\color{red}, %some words to emphasise
    %emph=[2]{word1,word2}, emphstyle=[2]{style},
}
\usepackage{color} %red, green, blue, yellow, cyan, magenta, black, white
\definecolor{mygreen}{RGB}{28,172,0} % color values Red, Green, Blue
\definecolor{mylilas}{RGB}{170,55,241}

\usepackage{siunitx}
\newcommand{\e}[1]{\times 10^{#1}} % nicer scientific notation

\title{ENV-541 Sensor Orientation\\Lab 7 - Kalman Filtering with simulated GPS data: simple (a=0) model}
\author{Michael Spieler}
\date{November 9, 2018}

\begin{document}

\maketitle

\section*{Questions}

\subsubsection*{I. What is the true overall improvement of the positioning accuracy by the filtering
(i.e. through comparing $\sigma_{xy}^{KF_{emp.}}$ versus $\sigma_{xy}^{GPS_{emp.}}$).}

\subsubsection*{II. How many measurements does it take to stabilize the predicted accuracy in position?}

\subsubsection*{III. Does the evolution of the predicted positioning accuracy depend on the actual measurements?
If yes, why is that? If no, why is that?}

\subsubsection*{IV. How well does the empirically estimated position accuracy ( $\sigma_{xy}^{KF_{emp.}}$)
correspond to the anticipated/predicted accuracy ( $\sigma_{xy}^{KF_{emp.}}$ ) and which parameters
of the filter would you suggest modifying to improve the agreement?}

\newpage
\section*{Code}
\lstinputlisting{../lab7.m}

\end{document}
