\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{float}
\usepackage{subcaption}
\usepackage{geometry}
\geometry{
    a4paper,
    total={170mm,257mm},
    left=20mm,
    right=20mm,
    top=20mm,
}
\usepackage{listings} % code listings
\lstset{framextopmargin=0pt,frame=lines}
\lstset{
    language=Matlab,
    basicstyle=\footnotesize\ttfamily,
    breaklines=true,
    tabsize=4,
    keepspaces=true,
    columns=flexible,
    % backgroundcolor=\color[gray]{0.9},
    frame=single,
    breaklines=true,%
    morekeywords={matlab2tikz},
    keywordstyle=\color{blue},%
    morekeywords=[2]{1}, keywordstyle=[2]{\color{black}},
    identifierstyle=\color{black},%
    stringstyle=\color{mylilas},
    commentstyle=\color{mygreen},%
    showstringspaces=false,%without this there will be a symbol in the places where there is a space
    numbers=left,
    numberstyle={\tiny \color{black}},% size of the numbers
    numbersep=9pt, % this defines how far the numbers are from the text
    emph=[1]{for,end,break},emphstyle=[1]\color{red}, %some words to emphasise
    %emph=[2]{word1,word2}, emphstyle=[2]{style},
}
\usepackage{color} %red, green, blue, yellow, cyan, magenta, black, white
\definecolor{mygreen}{RGB}{28,172,0} % color values Red, Green, Blue
\definecolor{mylilas}{RGB}{170,55,241}

\usepackage{siunitx}
\newcommand{\e}[1]{\times 10^{#1}} % nicer scientific notation

\title{ENV-541 Sensor Orientation\\Lab 8 - Kalman Filtering with simulated GPS data: constant acceleration (a = const.) model}
\author{Michael Spieler}
\date{November 23, 2018}

\begin{document}

\maketitle

\section*{Plots}

\section*{Questions}


\subsubsection*{I. Is the overall improvement of the \textit{positioning accuracy} via KF filtering better with
respect to the model of constant velocity (i.e. plot/compare $\sigma_{xy}^{KF_{emp.}}$ versus $\sigma_{xy}^{GPS_{emp.}}$)?
If yes/no – what do you think is the reason?}

\subsubsection*{II. Is the \textit{anticipated accuracy} ($\sigma_{xy}^{KF_{p}}$) different from that of the model of constant
velocity? Provide a justification.}

\subsubsection*{III. How does the \textit{distribution of velocity errors} ($v^{true} – v^{KF}$) compare to that obtained
with the constant velocity model? Can you identify and explain a pattern in these
differences for the model of constant acceleration?}

\subsubsection*{IV. Do the plotted histograms of innovations look like a normal distribution (visually)?
If yes/no, which case (from A or B in Task 4.4) is closer to normality and why?}

\subsubsection*{V. Do you observe statistically significant changes for the position or velocity
empirical or anticipated accuracies when using \textit{faster prediction} (i.e. $dt_{KF}=0.1s$ vs.
$dt_{KF}=1s$)? \textit{Justify} your answer by reasoning.}

\subsubsection*{VI. Observe what happens when you first increase and then decrease the given value of
the system noise level ($\sigma_{\dot a}$) 10 times. How do you interpret the observed changes
in the filtered positions, velocities and the distribution of innovation, respectively?}

\newpage
\section*{Code}
\lstinputlisting{../lab8.m}

\end{document}
